Pillar A1

### 2019-02-18 Baby Recommender.Rmd

@@

# TO DO: basic- doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
##Matching rules to students:
###Taken
```{r will take}
# very basic, doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
taken_match <- AR$taken %>%
  full_join(sample_transcript, by = c("lhs"="item"))%>%
  drop_na() %>%
  group_by(sequenceID, rhs) %>%
  summarise(RHS_vote= n())  %>%
  arrange(sequenceID,desc(RHS_vote))

recommendations <- taken_match %>%
  group_by(sequenceID)         %>%
  filter(row_number(RHS_vote) %in% 1:3) %>% #can use top_n
  arrange(sequenceID)          %>%
  select(sequenceID, RHS_vote, everything())

@@

```
####Check
```{r evaluation}
recommendations %>%
  full_join(prospective_transcript, 
            by= c("sequenceID"="sequenceID","rhs"="item")
            ) %>% # this should not be left join.
  drop_na()
```

###PF
```{r prospective red flag}
prospective_RedFlag <- AR$PF %>%
  left_join(prospective_courses, by = c("lhs"="item_PF"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

```
###HL
```{r expected low result}
expect_low_result <- AR$HL  %>%
  left_join(prospective_courses, by = c("lhs"="item_HL"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))
```

##Matching sequences to students
###Taken
```{r will take}
d_suggestions<- SR$taken %>%
  left_join(sample_transcript, by = c("lhs"="item"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

>>>>

#TO DO: prepare variables at begining

@@

# TO DO: basic- doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
##Matching rules to students:
###Taken
```{r will take}
# very basic, doesn't look at confidence or lift:
#(*) Do the filtering for meaningful rules first. 
#(**)Exclude taken already from the rhs.
taken_match <- AR$taken %>%
  #DO FILTERING FOR MEANINGFUL RULES HERE
  full_join(sample_transcript, by = c("lhs"="item"))%>%
  select(sequenceID, lhs, rhs) %>%
  drop_na() %>% #we lose 20 courses here -->20 rules or students are not matched with the transcripts
  group_by(sequenceID, rhs) %>%
  summarise(RHS_vote= n())  %>%
  arrange(sequenceID,desc(RHS_vote))

recommendations <- taken_match %>%
  group_by(sequenceID)         %>%
  filter(row_number() %in% 1:3) %>% #can use top_n
  arrange(sequenceID)          %>%
  select(sequenceID, RHS_vote, everything())

@@

```
####Check
```{r evaluation}
recommendations %>%
  full_join(prospective_transcript, 
            by= c("sequenceID"="sequenceID","rhs"="item")
            ) %>%
  drop_na()
```

###PF
```{r prospective red flag}
prospective_RedFlag <- AR$PF %>%
  left_join(prospective_courses, by = c("lhs"="item_PF"))%>%
  select(sequenceID, lhs, rhs) %>%
  drop_na() %>% #we eliminate rules that don't match students
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

prospective_RedFlag
```
###HL
```{r expected low result}
expect_low_result <- AR$HL  %>%
  left_join(prospective_courses, by = c("lhs"="item_HL"))%>%
  select(sequenceID, lhs, rhs) %>%
  drop_na() %>% #we eliminate rules that don't match students
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

expect_low_result
```

###
```{r merging all}
#
#setup: cleaning before merge
RedFlag <- prospective_RedFlag %>%
  select(sequenceID,lhs, rhs) %>%
  separate(rhs, into = c("prospective_item","expected_PF") ) %>%
  mutate(transcript_type = "RedFlag",
         Precedent_PF= lhs)%>%
  select(-lhs)

Low_Results <- expect_low_result %>%
  select(sequenceID,lhs, rhs) %>%
  separate(rhs, into = c("prospective_item","expected_HL") ) %>%
  mutate(transcript_type = "LowResults" ,
          Precedent_HL= lhs)%>%
  select(-lhs)

prosp_transcript <- prospective_transcript %>%
  select(sequenceID, item) %>%
  mutate(transcript_type = "StudentChoice" )

#
#Join
recommender <- recommendations %>%
  mutate(transcript_type ="Recommendations" #,
         #Reason = paste("votes = ", RHS_vote, sep = "") #this should be moved to the end and be calculated with a case_when
         ) %>% 
  full_join(prosp_transcript, by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "item") )             %>%
  full_join(RedFlag,          by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "prospective_item") ) %>%
  full_join(Low_Results,      by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "prospective_item") ) %>%
  mutate(Reason = case_when(
   transcript_type=="Recommendations"~ RHS_vote,
   transcript_type=="RedFlag"        ~ expected_PF,
   transcript_type=="LowResults"     ~ expencted_,
   transcript_type=="StudentChoice"
  ))

```
##Matching sequences to students
###Taken
```{r will take}
d_suggestions<- SR$taken %>%
  left_join(sample_transcript, by = c("lhs"="item"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))
